Not `Won't you be my neighbor?' \\ But `Should you be my neighbor?'

### 2014-12-15 paper_skeleton.tex
im about to try to write about the relationship between correlation length and ESS strategies

These opposing forces caused by the costs of paying attention to more uninformed neighbors and the costs of not paying attention to informed neighbors also explains the second feature of the ESS strategies: they are non-monotonic with respect to the the radius of the signal, i.e. how public the signal is (Figure \ref{ESS}).

%The ESS strategies when selection is due to knowledge about predators show two interesting features. First, there are many parameters for which there are multiple ESS strategies. For example, when the radius of the signal is $r=0.1$, the strategies of having fourteen, fifteen, sixteen, or seventeen neighbors are all ESS. This means that if the group is made up entirely of individuals having sixteen neighbors, then a mutant with any other strategy, including having seventeen neighbors, cannot invade. But if we instead consider a group made up entirely of individuals having seventeen neighbors, then a mutant with sixteen cannot invade either. This is because the success of any individual, resident or mutant, is strongly dependent on the environment set by the resident strategy.  In general, if a focal bird has several informed neighbors (and does not have the signal itself), then its uninformed neighbors decrease the focal bird's performance and make it more likely to be eaten. Thus, for a given number of informed neighbors, having more neighbors rather than fewer is a worse strategy. On the other hand, it a focal bird has no informed neighbors, then averaging the naive opinions of more neighbors rather than fewer makes it more likely for it pick up some information about the signal and avoid being eaten. In Figure \ref{ESS} we show that a bird with seventeen neighbors is more likely to be eaten when it has informed neighbors than a bird with sixteen neighbors but less likely to be eaten when it has no informed neighbors. The magnitudes of these opposing effects---the cost of more naive neighbors when a bird has informed neighbors and the benefit of more naive neighbors when a bird has no informed neighbors---depend on how the rest of the group is gathering information. When the resident strategy is lower, e.g. sixteen, the noise picked up by a mutant with seventeen neighbors at an intermediate number of informed neighbors makes it very likely to be eaten in those situations. Conversely, when the resident strategy is higher, e.g. seventeen, the inability of a mutant with sixteen neighbors to pick up any information without informed neighbors makes it very likely to be eaten in those situations. For each radius of $r$ of the signal, these opposing forces equilibrate at different ESS strategies.
%
%The second feature of the ESS strategies is that they are non-monotonic with respect to the the radius of the signal, i.e. how public the signal is (Figure \ref{ESS}). This non-monotonic behavior is due to two opposing effects of paying attention to more neighbors. First, having more neighbors increases the probability that one of them will have the signal and thus the probability that the focal bird will have a good source of information. Second, having more neighbors increases the probability that a focal bird will be trying to learn from individuals who do not have true information about the environment. When few individuals have the true signal (i.e. low radius $r$), the second effect outweighs the first and the ESS strategies are to pay attention to fewer birds than are in the whole flock. However, as more individuals have the true signal (i.e. higher radius $r$), the first effect is more important.

@@

\section{Figures }
\begin{figure}[ht]
\includegraphics[width=6.83in]{/Users/eleanorbrush/Desktop/ESSfigure.pdf}
\caption{\label{ESS} The ESS number of neighbors is always higher if selection is due to predation than due to resources. When selection is due to predation, there can be multiple ESS strategies, which are a non-monotonic function of the radius of the signal. In (a), we show the (possibly multiple) ESS strategies as a function of the radius of the signal. In (b) and (c), each heat map shows the probability that an invader is eaten as a function of the number of informed birds in the flock on the horizontal axis and the number of informed neighbors the invader has on the vertical axis. In (b), the resident strategy is to have $16$ neighbors and the invader strategy is to have $17$ neighbors. In (c), the resident strategy is to have $17$ neighbors and the invader strategy is to have $16$ neighbors. Parameters:  in all panels $\beta=1$, $T=1$, in (b) and (c) $r=0.1$. 
}
\end{figure}

>>>>

These opposing forces caused by the costs of paying attention to more uninformed neighbors and the costs of not paying attention to informed neighbors also explains the second feature of the ESS strategies: they are non-monotonic with respect to the the radius of the signal, i.e. how public the signal is (Figure \ref{ESS}). Figure \ref{ESS} shows that there are essentially three categories of radii: When the radius is low, the signal is private, with only a few birds having true information. When the radius is intermediate, the signal is public, with many birds having true information. When the radius is high, the signal is universal, with essentially all birds in the flock having true information. When the signal is private, paying attention to too few birds is costly because with more neighbors it is more likely to have a truly informed neighbor, but paying attention to too many uninformed birds can also be costly. This leads to a high but not maximal ESS strategy. When the signal is public, the costs of paying attention to uninformed birds are reduced and the ESS strategy increases to become as high as possible. When the signal is universal, not paying attention to informed birds does not impose a cost. Additionally, in a group in which the residents pay attention to all of their neighbors, any mutant strategy can get just as much information by paying attention to fewer neighbors so the maximal strategy is no longer an ESS (Figure \ref{ESS}).

@@

expect single ESS strategies but social information depends on the social environment set by the resident strategy
expect ESS strategies to decrease as the signal becomes more public, but we find the opposite

\section{Figures }
\begin{figure}[ht]
\includegraphics[width=6.83in]{/Users/eleanorbrush/Desktop/ESSfigure.pdf}
\caption{\label{ESS} The ESS number of neighbors is always higher if selection is due to predation than due to resources. When selection is due to predation, there can be multiple ESS strategies, which are a non-monotonic function of the radius of the signal. In (a), we show the (possibly multiple) ESS strategies as a function of the radius of the signal. In (b) we show the probability of there being a given number of informed birds for signals with different radii. In (c) and (d), each heat map shows the probability that an invader is eaten as a function of the number of informed birds in the flock on the horizontal axis and the number of informed neighbors the invader has on the vertical axis. In (c), the resident strategy is to have $16$ neighbors and the invader strategy is to have $17$ neighbors. In (d), the resident strategy is to have $17$ neighbors and the invader strategy is to have $16$ neighbors. Parameters:  in all panels $\beta=1$, $T=1$, in (c) and (d) $r=0.1$. 
}
\end{figure}
